\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-07-22 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

We have also added the ability to run several calculations (several earthquakes)
in an embarrassingly-parallel fashion from within the same run;
this can be useful when using a very large supercomputer to compute
many earthquakes in a catalog, in which case it can be better from
a batch job submission point of few to start fewer and much larger jobs,
each of them computing several earthquakes in parallel.
To turn that option on, set parameter NUMBER\_OF\_SIMULTANEOUS\_RUNS
to a value greater than 1 in file setup/constants.h.in before
configuring and compiling the code.
When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of NUMBER\_OF\_SIMULTANEOUS\_RUNS,
all the individual runs must use the same number of processor cores
(which as usual is NPROC in the input file DATA/Par\_file,
and thus the total number of processor cores to request from the batch system
should be NUMBER\_OF\_SIMULTANEOUS\_RUNS * NPROC.
All the runs to perform must be placed in directories called run0001, run0002, run0003 and so on (with exactly four digits).

>>>>

We have also added the ability to run several calculations (several earthquakes)
in an embarrassingly-parallel fashion from within the same run;
this can be useful when using a very large supercomputer to compute
many earthquakes in a catalog, in which case it can be better from
a batch job submission point of view to start fewer and much larger jobs,
each of them computing several earthquakes in parallel.
To turn that option on, set parameter NUMBER\_OF\_SIMULTANEOUS\_RUNS
to a value greater than 1 in file setup/constants.h.in before
configuring and compiling the code.
When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of NUMBER\_OF\_SIMULTANEOUS\_RUNS,
all the individual runs must use the same number of processor cores,
which as usual is NPROC in the input file DATA/Par\_file,
and thus the total number of processor cores to request from the batch system
should be NUMBER\_OF\_SIMULTANEOUS\_RUNS $\times$ NPROC.
All the runs to perform must be placed in directories called run0001, run0002, run0003 and so on (with exactly four digits)
and you must create a link from the root directory of the code
to the first copy of the executable programs by typing " ln -s run0001/bin bin ".
